% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode

\documentclass[a4paper]{limecv}

% Defaults used in template design.
\usepackage[margin=\cvMargin,noheadfoot]{geometry}

% For cover letter.
\usepackage{lipsum}

\begin{document}

\cvSetLanguage{english}

% Design of side bar.
\begin{cvSidebar}
  \cvID{\textbf{Joseph}}{\textbf{Haughey}}{}{Business Graduate}

  \begin{cvProfile}
    Hard working, ambitious, and enthusiastic BSc Hons Business Studies
    graduate seeking challenging and enjoyable opportunies.\\
    A loyal and dedicated team player with excellent interpersonal 
    skills and a desire to learn and grow professionally.
  \end{cvProfile}
  
  \begin{cvContact}
    \cvContactAddress{Lurgan, Co. Armagh}
    \cvContactPhone{+44 78564 85251}
    \cvContactEmail{mailto:joseph@haughey.dev}{joseph@haughey.dev}
    \cvContactGithub{https://github.com/johaughey}{johaughey}
    \cvContactLinkedin{https://www.linkedin.com/in/joseph-haughey-265874108}{joseph-haughey}
  \end{cvContact}

  \begin{cvReferencesSB}
    Available on request
  \end{cvReferencesSB}

\end{cvSidebar}

\begin{cvMainContent}

  \begin{cvExperience}
    \cvItem{
    \textbf{Shift Manager}, 
    \textsc{\selectfont \href{https://www.mcdonalds.com/gb/en-gb.html}{McDonald's}}, Rushmere Shopping Centre\hfill 
    \emph{<when?> - pres}\\
    After being promoted to the position of shift manager I have over 
    time taken on more responsibility, and have proven that I am someone
    who can be relied upon and will not shy away from a heavy workload.\\
    Being a shift manager has taught me the importance of being 
    adaptable and flexible, having a strong work ethic, good 
    communication skills and the ability to manage time effectively. It
    has allowed me to develop various skills whist regularly being in
    charge of a team of 25-30 people.\\
    I have been given the responsibility of training other members of
    staff on different areas, including service, kitchen and backroom I
    feel I have been able to excel in training other staff because of my
    strong attention to detail. This has required me to be flexible and
    adaptable within my own role.
    };
    \cvItem{
    \textbf{Area Leader}, 
    \textsc{\selectfont \href{https://www.mcdonalds.com/gb/en-gb.html}{McDonald's}}, Rushmere Shopping Centre\hfill 
    \emph{<when?>}\\
    As an area leader I have been tasked with leading groups of staff
    within McDonalds. To do this effectively and efficiently, I had to
    liaise with my colleagues and understand what their own personal
    strengths were. This allowed me the develop my leadership qualities
    within a professional environment.
    };
    \cvItem{
    \textbf{Crew Member}, 
    \textsc{\selectfont \href{https://www.mcdonalds.com/gb/en-gb.html}{McDonald's}}, Rushmere Shopping Centre\hfill 
    \emph{Oct12 - <when?>}\\
    <Start by stating duties in the form: "Verbed something something blah blah 
    blah." Do a couple of these, as sentences as if they're bullet
    points. Then say what you learned/gained/got experience in.>
    Dealing with customer queries and complaints has also helped me to
    develop my problem solving skills. Working in service has also
    helped me to develop my interpersonal and communication skills.
    };
    \cvItem{
    \textbf{Sales Adviser}, 
    \textsc{\selectfont \href{https://www.argos.co.uk}{Argos}}, Rushmere Shopping Centre\hfill 
    \emph{Oct11 - Feb12}\\
    Seasonal role over the busy Christmas period. Primary role involved
    retrieving products from stockroom shelves for customers. Other
    duties included <tills? restocking? Try for 2 examples here>.
    Developed my ability to work under pressure, and learned how to 
    communicate effectively with teammates in a fast-paced environment.
    };  
    \cvItem{
    \textbf{Work Experience}, 
    \textsc{\selectfont Northern Ireland Civil Service}\hfill 
    \emph{Aug12}\\
    <N> week development session, mainly focused in the Department for
    <X>, with overlap into related departments <(such as)>.
    Gained experience working in an office environment, learned IT
    productivity tools such as Outlook and <Y>, and had the opportunity
    to meet people in various roles \& teams.
    };  
  \end{cvExperience}

  \begin{cvEducation}
    \cvItem{\textbf{BSc Hons Business Studies}, Ulster University, Jordanstown\hfill \emph{2015 - 2017}\\
      \emph{II.2}\\
      \emph{Operations Management, Marketing Communications, E-Business, Accounting for Business Decisions, Strategic HRM, Managing People}
      }
    \cvItem{\textbf{BTEC Level 5 HND, Business Studies}, Belfast Metropolitan College\hfill \emph{2013 - 2015}\\
      \emph{Merit}\\
      \emph{Business Environment, Managing Financial Resources, Internet Marketing}
      }    
    \cvItem{\textbf{A Level}, St Michael's Grammar School, Co. Armagh\hfill \emph{2011 - 2013}\\
      History \emph{(B)}, Religion \emph{(B)}, Business Studies \emph{(C)}}
    \cvItem{\textbf{GCSE}, St Michael's Grammar School, Co. Armagh\hfill \emph{2009 - 2011}\\
      A \emph{(2)}, B \emph{(4)}, C \emph{(3)}}
  \end{cvEducation}

  \begin{cvSkills2}
    \cvItemTwo{
      \textbf{Problem solving:}
        <Be more direct here, just state an example or two of you 
        demonstrating this skill, or where you learned it. E.g.
        Dealing with customer queries, staff timetabling, and stock 
        shortages in my role as Shift Manager. Max 2 lines (in the PDF),
        including the bolded title point.>
        Working in the kitchen in McDonald’s can be hectic at times, as
        it is a fast-paced environment, and problems consistently arise,
        whether its a shortage of stock, a shortage of staff, or
        just overly busy.
    }
    \cvItemTwo{
      \textbf{Attention to detail:}
        As a shift manager in McDonald’s I have been put in charge of
        ordering for the store. <<I required>> to ensure that we
        have the right amount of stock in store to meet demand while
        adhereing to food cost limits. The role has also required me
        to be conscious of date-sensitive items.
    }
    \cvItemTwo{
      \textbf{Teamwork:}
        Through playing Gaelic football and soccer throughout my youth I
        have learnt the importance of teamwork and dedication.
        During my Under 14 year I was made vice captain of my Gaelic
        Football team, Clann Eireann.
    }
    \cvItemTwo{
      \textbf{Organisation:}
        I am a very organised person by nature. Despite that, I feel as
        though I developed this skill a lot whilst completing my GCSE’s
        at St Michael’s Grammar School, by balancing several activities
        such as playing both gaelic and
        soccer at both club and schools level, having a part time job at
        the weekends and keeping a healthy social life.   
    }

  \end{cvSkills2}


\end{cvMainContent}

\clearpage

\end{document}